Supplemental Materials, Methods and Results

### 2022-04-21 supp/Supplemental Materials and Methods.Rmd
Changed name for pivot longer value

        ################ THIS SHOULD FIX THE DATA_LONG problems
      data_long <- data_wide %>%
                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% 
                    mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()

>>>>

        ################ THIS SHOULD FIX THE DATA_LONG problems
      data_long <- data_wide %>%
                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43), values_to = "effect_size", values_drop_na = FALSE) %>% 
                    mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()
